Sensitivity Analysis

### 2024-03-19 SFE_article_Sensitivity_Analysis - Chamomile/Sections/Results_Sensitivity.tex
19.03

	This work investigates the influence of inlet temperature, pressure, and mass flow rate on the state space and the extraction yield. The process model and parameters have been discussed in {\color{red}article 1}. The process model was calibrated on the set of experiments obtained at different operating conditions, $40$ - $50^\circ C$ and 200 - 300 bar. The sensitivity analysis has been performed assuming that the system operates at $45^\circ C$, 250 bar and 0.4 l/min.

@@

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_F.pdf}
		\caption{The effect of $F$ change on $P$}
		\label{fig:Sensitivty_F_P}
	\end{figure}

@@

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_F.pdf}
    	\caption{The effect of $F$ change on $h \times \rho$}
    	\label{fig:Sensitivty_F_H}
    \end{figure}

@@

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.pdf}
    	\caption{The effect of $F$ change on $C_s$}
    	\label{fig:Sensitivty_F_CS}
    \end{figure}

@@

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.pdf}
    	\caption{The effect of $F$ change on $C_f$}
    	\label{fig:Sensitivty_F_CF}
    \end{figure}

@@

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_F.pdf}
    	\caption{The effect of $F$ change on $y(t)$}
    	\label{fig:Sensitivty_F_y}
    \end{figure}

@@

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_P.pdf}
    	\caption{The effect of $P$ change on $P$ in the system}
    	\label{fig:Sensitivty_P_P}
    \end{figure}

@@

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_P.pdf}
    	\caption{The effect of $P$ change on $(h \times \rho)$ in the system}
    	\label{fig:Sensitivty_P_H}
    \end{figure}

@@

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.pdf}
		\caption{The effect of $P$ change on $C_s$}
		\label{fig:Sensitivty_P_CS}
	\end{figure}

@@

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.pdf}
		\caption{The effect of $P$ change on $C_f$}
		\label{fig:Sensitivty_P_CF}
	\end{figure}

@@

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_P.pdf}
		\caption{The effect of $P$ change on $y(t)$}
		\label{fig:Sensitivty_P_y}
	\end{figure}

@@

	The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through the system. As the fluid with the modified temperature flows along the system, it gradually modifies the mass transfer parameters. One important assumption is that the inlet temperature change does not affect the pressure, which explains a horizontal line in Figure \ref{fig:Sensitivty_P_T}.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_T_{in}.pdf}
		\caption{The effect of $T_{in}$ change on $P$ in the system}
		\label{fig:Sensitivty_P_T}
	\end{figure}

	The heat front propagation is presented in Figure \ref{fig:Sensitivty_T_H}. The initial system had constant temperature along the whole spatial domain. The inlet temperature is a control characterized by the Dirichlet boundary condition. The boundary value of $(h\times \rho)$ is calculated based on two controls which can be manipulated: inlet temperature and given pressure. Any deviation in $T_{in}$ affects $(h\times \rho)$ at the inlet, propagating according to the governing equations.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_T_{in}.pdf}
		\caption{The effect of $T_{in}$ change on $(h \times \rho)$ in the system}
		\label{fig:Sensitivty_T_H}
	\end{figure}

	Figure \ref{fig:Sensitivty_T_CS} illustrates how the change in inlet temperature affects the concentration of solute in the solid phase. As presented in {\color{red}article 1}, the value of $D_i^R$ decreases as density decreases. Therefore, it is expected to observe positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, indicating a slower extraction rate. Initially, the sensitivities are zero along the fixed bed because the heat front requires time to reach the fixed bed. Since this propagation is not instantaneous, a non-uniform distribution of sensitivities along the fixed bed becomes evident. All the sensitivities gradually increase until they reach their maximum. When the concentration gradient becomes the limiting factor, the sensitivities decrease.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_T_{in}.pdf}
		\caption{The effect of $T_{in}$ change on $C_s$ in the system}
		\label{fig:Sensitivty_T_CS}
	\end{figure}

	The influence of inlet temperature on solute concentration in the fluid phase is depicted in Figure \ref{fig:Sensitivty_T_CF}. Initially, all the sensitivities remain at zero due to the idle period. As the fluid with elevated temperature flows through the fixed bed, the internal mass transfer slows down (the $D_i^R$ is proportional to density as presented in {\color{red}article 1}), resulting in negative sensitivities. The diffusion effect is observable in the empty section, where the front composed of sensitivities becomes blurry. After reaching their minima, the sensitivities increase and reach slightly positive values. This behaviour can be explained by considering that the heat front slowed mass transfer, causing more solute to remain in the solid phase.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_T_{in}.pdf}
		\caption{The effect of $T_{in}$ change on $C_f$ in the system}
		\label{fig:Sensitivty_T_CF}
	\end{figure}

@@

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 1.5cm 1cm 0.0cm 1.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_T_{in}.pdf}
		\caption{The effect of $T_{in}$ change on $y(t)$ in the system}
		\label{fig:Sensitivty_T_y}
	\end{figure}

>>>>

	This work investigates the influence of inlet temperature, pressure, and mass flow rate on the state space and the extraction yield. The process model and parameters have been discussed in {\color{red}article 1}. The process model was calibrated on the set of experiments obtained at different operating conditions, $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \times 10^{-5}$ kg/s. The sensitivity analysis has been performed assuming that the system operates at $35^\circ C$, 150 bar and 5 $\times 10^{-5}$ kg/s.

@@

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_F.png}
		\caption{The effect of $F$ change on $P$}
		\label{fig:Sensitivty_F_P}
	\end{figure}

@@

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_F.png}
    	\caption{The effect of $F$ change on $h \times \rho$}
    	\label{fig:Sensitivty_F_H}
    \end{figure}

@@

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.png}
    	\caption{The effect of $F$ change on $C_s$}
    	\label{fig:Sensitivty_F_CS}
    \end{figure}

@@

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.png}
    	\caption{The effect of $F$ change on $C_f$}
    	\label{fig:Sensitivty_F_CF}
    \end{figure}

@@

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_F.png}
    	\caption{The effect of $F$ change on $y(t)$}
    	\label{fig:Sensitivty_F_y}
    \end{figure}

@@

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_P.png}
    	\caption{The effect of $P$ change on $P$ in the system}
    	\label{fig:Sensitivty_P_P}
    \end{figure}

@@

    \begin{figure}[h!]
    	\centering
    	\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_P.png}
    	\caption{The effect of $P$ change on $(h \times \rho)$ in the system}
    	\label{fig:Sensitivty_P_H}
    \end{figure}

@@

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.png}
		\caption{The effect of $P$ change on $C_s$}
		\label{fig:Sensitivty_P_CS}
	\end{figure}

@@

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.png}
		\caption{The effect of $P$ change on $C_f$}
		\label{fig:Sensitivty_P_CF}
	\end{figure}

@@

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_P.png}
		\caption{The effect of $P$ change on $y(t)$}
		\label{fig:Sensitivty_P_y}
	\end{figure}

@@

	The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through the system.

	The Figure \ref{fig:Sensitivty_P_T} for the system pressure response shows a flat curve, indicating an invariant behavior of pressure in response to inlet temperature changes throughout the time. This uniformity is expected, as explained in the Chapter XXX. The pressure of the modelled system is controlled and maintained independently of the inlet temperature variations. 
	%The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through the system. As the fluid with the modified temperature flows along the system, it gradually modifies the mass transfer parameters. One important assumption is that the inlet temperature change does not affect the pressure, which explains a horizontal line in Figure \ref{fig:Sensitivty_P_T}.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_T_{in}.png}
		\caption{The effect of $T_{in}$ change on $P$ in the system}
		\label{fig:Sensitivty_P_T}
	\end{figure}

	The inlet temperature is characterized by the Dirichlet boundary condition. The boundary value of $(h\times \rho)$ is calculated based on two controls which can be manipulated: inlet temperature and given pressure. Any deviation in $T_{in}$ affects $(h\times \rho)$ at the inlet, propagating according to the governing equations.
	Figure \ref{fig:Sensitivty_T_H} showcases the sensitivity of the fluid enthalpy to the inlet temperature over both time and the length of the extraction bed. The heat front propagation from the inlet of the extractor to its outlet. The fluid entering the extraction bed will have its enthalpy most influenced by the inlet conditions. As the fluid progresses through the bed, the enthalpy change sensitivity affects the whole system gradually. Over time, the system's gradual approach to a new thermal steady state and the sensitivities becomes zero.

	%The heat front propagation is presented in Figure \ref{fig:Sensitivty_T_H}. The initial system had constant temperature along the whole spatial domain.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_T_{in}.png}
		\caption{The effect of $T_{in}$ change on $(h \times \rho)$ in the system}
		\label{fig:Sensitivty_T_H}
	\end{figure}

	Figure \ref{fig:Sensitivty_T_CS} shows the curve depicts an initial sharp increase (positive sign of the sensitivities) in the solute concentration in the solid phase as a function of time, which then asymptotically approaches a stable value before increasing again towards the end of the period. Although $D_i^R$ decrease with the fluid's density, the $\Upsilon$ increases, which explains the system responses. This suggests that an increase in inlet temperature initially slow down the mass transfer of solutes from the solid phase to the supercritical fluid, hence the concentration of the solute in the solid phase increases. Over time, this effect stabilizes, which could indicate the exhaustion of easily extractable solutes.
	%Figure \ref{fig:Sensitivty_T_CS} illustrates how the change in inlet temperature affects the concentration of solute in the solid phase. As presented in {\color{red}article 1}, the value of $D_i^R$ decreases as density decreases. Therefore, it is expected to observe positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, indicating a slower extraction rate. Initially, the sensitivities are zero along the fixed bed because the heat front requires time to reach the fixed bed. Since this propagation is not instantaneous, a non-uniform distribution of sensitivities along the fixed bed becomes evident. All the sensitivities gradually increase until they reach their maximum. When the concentration gradient becomes the limiting factor, the sensitivities decrease.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_T_{in}.png}
		\caption{The effect of $T_{in}$ change on $C_s$ in the system}
		\label{fig:Sensitivty_T_CS}
	\end{figure}

	The Figure \ref{fig:Sensitivty_T_CF} represents the sensitivity of the concentration of solutes in the fluid phase over a period of 600 minutes as a result of changes in the inlet temperature. Initially, all the sensitivities remain at zero due to the idle period. As the fluid with elevated temperature flows through the fixed bed, the internal mass transfer slows down (the $D_i^R$ is proportional to density as presented in {\color{red}article 1}), resulting in negative sensitivities. The negative sensitivities can be explained by considering that the heat front slowed mass transfer, causing more solute to remain in the solid phase. After reaching their minima, the sensitivities increase and reach positive values. Later the sensitivities starts to increase due higher concentration gradient if compared to before the temperature change. Eventually, the system response stabilize around a constant value when the extraction kinetics become a limiting factor.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_T_{in}.png}
		\caption{The effect of $T_{in}$ change on $C_f$ in the system}
		\label{fig:Sensitivty_T_CF}
	\end{figure}

@@

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_T_{in}.png}
		\caption{The effect of $T_{in}$ change on $y(t)$ in the system}
		\label{fig:Sensitivty_T_y}
	\end{figure}
